Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-06-19 Thesis/chapter/03-theoretical-background.tex
DOE

\subsubsection{different kinds} 
supervised vs unsupervised
classification (discrete) vs regression
%
\subsubsection{Particle Swarm Optimization}
%
\subsubsection{Princlipal Component Analysis}
reinforcement learning could also have been a nice option
%
\subsubsection{Linear Regression}
%

>>>>

\subsubsection{different kinds} 
supervised vs unsupervised
classification (discrete) vs regression
%
\subsubsection{Particle Swarm Optimization}
%
\subsubsection{Princlipal Component Analysis}
reinforcement learning could also have been a nice option
%
\subsubsection{Linear Regression}
%
\subsubsection{2022-06-19-Free-Writing}
The problem which presents it self is in principle a search problem.
A large space of possible combinations of experimental anordnungen presents it self
and out of these we want to find the optimial parameter combination. 
The best way with unlimitied resources would be the brute-force approach to try every possibility. 
But due to limited time this is unfeasable. 
But a new questions arises: how should the ausmasse of the search space be eingeschraenkt? 
What are the upper and lower limits and which intervals/step size/grid size should be used. 
Also even before, we have to answer which dimensions/parameters should we include in the search? 
Which parameters should we keep constant and at which value? 
And finally which features should we use to measure the goodness of an experiment?

I tried different methods to answer the first X questions: Latin square and Plackett-Burman design.
Unfortunately, I was faced with similar questions. How many levels and which end points? 
latin squares are about orthogonality 
PB is a factorial experiment desing in contrast to one-fator-at-a-time methods.
reliability and validity are low due to experiments not replicated

https://en.wikipedia.org/wiki/Design_of_experiments
https://en.wikipedia.org/wiki/The_Design_of_Experiments
https://en.wikipedia.org/wiki/Response_surface_methodology
https://en.wikipedia.org/wiki/Optimal_design
https://sci-hub.st/https://doi.org/10.2307/2332195
https://en.wikipedia.org/wiki/Latin_square
https://en.wikipedia.org/wiki/Outline_of_artificial_intelligence
https://en.wikipedia.org/wiki/Evolutionary_algorithm
https://en.wikipedia.org/wiki/Particle_swarm_optimization
EMMA doesn't allow for reproducibility
